### 2010-12-18 doc/tech_doc/a-rex/arex_tech_doc.tex
Adding VOMS elements into A-REX configuration example and VOMS-based authorization policy example

@@

      <!-- Evaluate requestor's identity into local identity.
      Comment it if no user mapping is needed. -->
        <idmap:PDP name="allow.pdp"><idmap:LocalName>nobody</idmap:LocalName></idmap:PDP>

@@

@@

>>>>

  xmlns:pdp="http://www.nordugrid.org/schemas/arcpdp/2009/08"

@@

      <!-- DNs of acceptable VOMS ACs -->
      <tls:VOMSCertTrustDNChain>
        <!-- Accept VOMS attributes from all sources -->
        <tls:VOMSCertTrustRegex>^.*$</tls:VOMSCertTrustRegex>
      </tls:VOMSCertTrustDNChain>

@@

      <!-- Performing authorization. Also see security documentation. -->
      <loader:SecHandler name="arc.authz" event="incoming">
        <authz:PDP name="arc.pdp">
          <pdp:Filter>
            <!-- Using only attributes comming from TLS (VOMS) and
                AREX (requested operations) -->
            <pdp:Select>TLS</pdp:Select>
            <pdp:Select>AREX</pdp:Select>
          </pdp:Filter>
          <pdp:PolicyStore>
            <!-- Type is currently not used. Only file is supported -->
            <pdp:Type>file</pdp:Type>
            <!-- Read and process policy from file. See policy 
                example in appendix. -->
            <pdp:Location>/opt/arc/etc/arex_policy.xml</pdp:Location>
          </pdp:PolicyStore>
        </authz:PDP>
      <!-- Evaluate requestor's Grid identity into local identity. -->
        <!-- Old bad mapfile -->
        <idmap:PDP name="allow.pdp">
          <idmap:LocalList>/etc/grid-security/grid-mapfile</idmap:LocalList>
        </idmap:PDP>
        <idmap:PDP name="allow.pdp">
          <idmap:LocalName>nobody</idmap:LocalName>
        </idmap:PDP>

@@

\section{Example of authorization policy for A-REX\label{annex:policy-example}}

\begin{footnotesize}\begin{verbatim}
<?xml version="1.0" encoding="UTF-8"?>
<Policy xmlns="http://www.nordugrid.org/schemas/policy-arc"
        PolicyId="policy:arex:example"
        CombiningAlg="Deny-Overrides">
   <Rule RuleId="knowarc.eu:serviceinfo" Effect="Permit">
      <Description>
         All who belongs to knowarc.eu VO can query information about service.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu</Subject>
      </Subjects>
      <Actions>
         <!-- AttributeId should be .../operation. But because of bug in A-REX this one is used. -->
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Info</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:admin" Effect="Permit">
      <Description>
         All developers belonging to knowarc.eu VO can manage service.
         This is useless rule because A-REX does not suport remote management.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=coredev</Subject>
      </Subjects>
      <Actions>
         <!-- AttributeId should be .../operation. But because of bug in A-REX this one is used. -->
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Admin</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:job" Effect="Permit">
      <Description>
         All testers of knowarc.eu VO can run jobs.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=testers</Subject>
      </Subjects>
      <Actions>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Create</Action>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Modify</Action>
         <Action AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/a-rex/joboperation">Read</Action>
      </Actions>
   </Rule>
   <Rule RuleId="knowarc.eu:all" Effect="Permit">
      <Description>
         All superusers of knowarc.eu VO can do anything.
      </Description>
      <Subjects>
         <Subject AttributeId="http://www.nordugrid.org/schemas/policy-arc/types/tls/vomsattribute">/VO=knowarc.eu/Group=superusers</Subject>
      </Subjects>
   </Rule>
</Policy>
\end{verbatim}
\end{footnotesize}
